Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Explain HTTP 400.

Fastly (\url{http://www.fastly.com/}) is a CDN.
It is unique among the the services we tested in that
it is the only one that appears to enforce the SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 error.
It is the only service we have found
that requires the ``domainless'' fronting style.

>>>>

Fastly (\url{http://www.fastly.com/}) is a CDN.
It is unique among the the services we tested in that
it is the only one that appears to enforce the SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
It is the only service we have found
that requires the ``domainless'' fronting style.
